---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


[![Travis-CI Build Status](https://travis-ci.org/dis-organization/depbioc.svg?branch=master)](https://travis-ci.org/dis-organization/depbioc)

How to depend on Bioconductor? 

The answer: http://stackoverflow.com/questions/14343817/cran-package-depends-on-bioconductor-package-installing-error

We have to do this: 

```{r,eval=FALSE}
source("http://bioconductor.org/biocLite.R")
```

Then add `biocViews:` to the DESCRIPTION, and the Imports/Suggests we need (`rhdf5` in Imports here and `BiocInstaller` and `zlibbioc` in Suggests). 


Then run these: 

```{r,eval=FALSE}
devtools::install_deps(dependencies = "Suggests")
devtools::install_deps(dependencies = "Imports")
```

Then this will work: 

```{r}
library(depbioc)
runa()
```

How to make this work on Travis? 

Needed `r: bioc-release` in travis.yml, despite this not being a Bioconductor package. 

https://docs.travis-ci.com/user/languages/

I don't see anything in Writing R Extensions, and the r-travis doc and the stackoverflow post above was what I needed. 

Appreciate any other known links. 


